---
title       : User's Data Analysis
subtitle    : An R app for analysis of small numeric data set   
author      : James
job         : Analyst
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

---
## About This App

1. Designed for analysis of user-generated data 
2. Powerful presentation using R 
3. Statistical analysis including t-test and ANOVA

--- 
## How to Use This App
1.  Upload your data
    * Selelct a data file using "Choose File" button
    * Select the "Header" checkbox if the file has headers
    * Check appropriate "separator" and "Qoute" radiobuttons 
   
   => Your raw data will appear on the "My Data" tab on the right-hand side
      To view the data, click on the "My Data" tab
   
2.  To select the plot, choose a plot type using the dropdown button in the "2.  Select the plot type".  
    * To view the plot, click on the "Presentation" tab on the right
    
3.  For statistical analysis select a test type using the dropdown button in "3. Select Statistical Analysis to be performed"
    * To view the result, click on the "Stat Test" tab

---
## Sample Data - Generate a data 
Use R to generate random numbers and a data frame as following:
```{r echo=TRUE}
library(reshape)
P <- round(rnorm(25, 8, 2.5), 2)
A <- round(rnorm(25, 10, 3), 2)
B <- round(rnorm(25, 11, 3.5), 2)
AB <- round(rnorm(25, 14, 3.5), 2)
combo <- data.frame(P, A, B, AB)
write.csv(combo, "combo.csv", row.names=FALSE)
melted <- melt(combo)
```
* "combo.csv" would be found in your R woring directory.  After you click the "Choose File" button, you have to go to this working directory to find the file.

---
## Sample "Presentation" Tab - Default; boxplot
```{r echo=FALSE}
summary(combo)
```
```{r echo=FALSE}
boxplot(combo)
```

---
## Sample "Stat Test" Tab - Default; t-test


```{r echo=FALSE}
pairwise.t.test(melted$value, melted$variable, paired = F, 
                                   alternative = "two.sided")
```